Kinematics of the Turtle Nebula

### 2020-03-03 turtle-paper.tex
Add a few lines to the abstract describing plans

\title{Kinematics of the Turtle Nebula (Will's part)}

@@

\begin{abstract}
  Material to be incorporated into the main paper by Teresa.
\end{abstract}
\begin{keywords}
  Atomic physics -- Radiative transfer -- Photodissociation regions
\end{keywords}

@@

>>>>

\title{Kinematics of the Turtle Nebula}

@@

\begin{abstract}
  Material to be incorporated into the main paper by Teresa. 
  This is now in a separate repo with just the paper, which is synced with Overleaf.  The plan is to merge it with Tere's draft.
\end{abstract}
\begin{keywords}
  Atomic physics -- Radiative transfer -- Photodissociation regions
\end{keywords}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{turtle-halo-map}
  \caption{
    Velocity components in the halo.
    Components are divided into three classes:
    inner halo (pink ellipses), outer halo (yellow ellipses),
    and halo knots (green ellipses).
  }
  \label{fig:halo-components}
\end{figure}
